\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-12 paper/main.tex
switched to using CDL bibliography, remove main.bib
switch conda citation for conda-forge

Within the Python~\citep{vanR95} community, external
packages that are published in the most popular
repositories~\citep{pypi, Anac12} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
\bibliographystyle{elsarticle-num}
\bibliography{main.bib}

>>>>

Within the Python~\citep{vanR95} community, external
packages that are published in the most popular
repositories~\citep{pypi, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
\bibliographystyle{elsarticle-num}
\bibliography{cdl}
